DRAFT

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

## • Summary for the main variables in the transformed dataset
## __Numeric variables__
```{r echo=FALSE}
datasummary(distance + starrating + actualrating + trueprice ~ Mean + Min + Max + SD, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

@@

### • Year and month
```{r echo=FALSE}
kable(count(df2, year))
```
```{r echo=FALSE}
kable(count(df2, month))
```
### • Accommodation type
```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n)))
```

@@

@@

### • Mean prices for diff seasons
```{r}
datasummary(trueprice*season ~ Mean, data=df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

### • Plot for classes
```{r message=FALSE}
datasummary(trueprice*class ~ Mean, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
ggplot(data = df2, aes(x=reorder(class, +trueprice), y=trueprice, fill = class)) + 
  geom_bar(stat = 'summary') + labs(x='Class', y='Price', fill = 'Class')
```

>>>>

## • Summary for the main variables in the transformed dataset
## *Numeric variables*
```{r echo=FALSE}
datasummary(distance + starrating + actualrating + trueprice ~ Mean + Min + Max + SD, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

@@

### • Year and month
```{r echo=FALSE}
kable(count(df2, year))
```
```{r echo=FALSE}
kable(count(df2, month))
```

### *Factor variables*

### • Accommodation type
```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n)))
```

@@

### *Binary variables*

@@

### • Mean prices for diff seasons
```{r echo=FALSE}
datasummary(trueprice*season ~ Mean, data=df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

### • Plot for classes
```{r echo=FALSE, message=FALSE}
datasummary(trueprice*class ~ Mean, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```
```{r echo=FALSE}
ggplot(data = df2, aes(x=reorder(class, +trueprice), y=trueprice, fill = class)) + 
  geom_bar(stat = 'summary') + labs(x='Class', y='Price', fill = 'Class')
```
